---
title: "Assessment 2"
author: "Karthik Revi s4644246"
date: "03/28/2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Part 1

*Karthik Revi*
## ID-s4644246 
<hr> 

# Assignment 2

<hr>
### Part 2

```{r}
install.packages("randomForest")
library(tidyverse)
library(skimr)


DATASET <-read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv")
```
### Question1
```{r}
knitr::kable(head(DATASET[,1:12],10))
```



### Question2
```{r}
dataset_new<-skim(DATASET)

```
### Question3
```{r}
family_income<-fct_reorder(DATASET$family_income, DATASET$family_income, min)
```



### Question 4
```{r}
nrow(subset(DATASET, celebrate=='Yes'))
```
### Question5
```{r}
knitr::kable(DATASET %>% group_by(main_dish) %>%  count(main_prep) %>% arrange(desc(n)) %>% head(n=10))
```
### Question6
```{r}
DATASET %>% ggplot() +  aes(x = main_dish, fill = main_dish) +   geom_bar() + labs(x = "Main Dish", y = "Count", title = "Main dish served method", subtitle = "Main Dish", caption = "main dish served method",  fill = "Legend")
```
<p>The most servered dish is Turkey clearly visible from the graph extracted using ggplot command</p>
<br>
### Question7
```{r}
nrow(subset(DATASET, cranberry=='Canned' | cranberry=='Homemade'))
nrow(subset(DATASET, gravy=='Yes'))
```

### Question 8 and 9
```{r}
knitr::kable(DATASET %>% group_by(celebrate) %>%  count(family_income) %>% arrange(desc(n)) %>% head(n=10))
```
```{r}
DATASET %>% ggplot() +  aes(x = celebrate, fill =family_income) +   geom_bar() + labs(x = "celebrate", y = "Count", title = "Distribution celebrate Income ranges", subtitle = "Celebrate", caption = "Distribution celebrate with income ranges",  fill = "Legend")
```
<p>The graph generated using ggplot command is showing that people irrespective of the income are celebrating</p>
<br>
### Question10
```{r}
dataset_new1<-DATASET %>% select(id, starts_with("side"),
         starts_with("pie"),
         starts_with("dessert")) %>%
  select(-side15, -pie13, -dessert12) %>%
  gather(type, value, -id) %>%
  filter(!is.na(value),
         !value %in% c("None", "Other (please specify)")) %>%
  mutate(type = str_remove(type, "\\d+"))
print(dataset_new1)
```
<p>The whole set of code lines extract three fields having value started with specific word</p>
<br>

### Question11 and 12
```{r}
library(widyr)
```
<p>The useful results are extrated from the query. The highest corrlation value is between Cookies and Brownies. The lowest correlation between the Mashed potatoes and Pumpkin</p>
<br>
```{r}
dataset_new1 %>% pairwise_cor(value, id, sort = TRUE)
```
<p>The useful results are extrated from the query. The highest corrlation value is between Cookies and Brownies. The lowest correlation between the Mashed potatoes and Pumpkin</p>
<br>
 
### Question 13

```{r}
dataset_new <- do.call(data.frame, lapply(dataset_new, function(x) {
  replace(x, is.infinite(x) | is.na(x) | is.nan(x), 0)
  })
)
datavalues <- lm(t(dataset_new[3])~t(dataset_new[4]),data =head(dataset_new,10))
summary(datavalues)

datavalues <- lm(t(dataset_new[5])~t(dataset_new[4]),data =head(dataset_new,10))
summary(datavalues)


datavalues <- lm(t(dataset_new[4])~t(dataset_new[3]),data =head(dataset_new,10))
summary(datavalues)
```
<p>The linear regression model is developed between different fields. All the fields are specifying the relation with regression model. The linear equation for prediction can also be evaluated</p>

<p> The selected model is having higher productivity and lower error rate.</p>



